Fusing Filters with Integer Linear Programming

### 2014-04-22 2014betterfusionforfilters/section/03-SizeInference.tex
size inf

Similarly, this example:
\begin{tabbing}
@MMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMM@  \= \kill
@bad2 vs@                           \> $\exists k_{vs}.$ \\
@ = let flt  = filter p  vs@        \> $\forall k_{flt}.$ \\
@       flt2 = filter p' vs@        \> $\forall k_{flt2}.$ \\
@       mix  = map2   f  flt flt2@  \> $\exists k_{mix}.\ k_{mix} = k_{flt}$ \\
                                    \> $\wedge k_{mix} = k_{flt2} \wedge$ \\
@   in  mix@                        \> $true$                               \\
\end{tabbing}
Again, transitivity here requires that $Filtered_{flt} = Filtered_{flt2}$, but since these are both concrete constructors, we cannot have such a constraint.
Basically, we are constraining two different filtered outputs to be the same size.
Operationally, implementing this would require to buffer both @flt@ and @flt2@, before checking the two lengths.

>>>>

Similarly, this example is not allowed, as it would require a runtime check to determine that the output of two filters @flt@ and @flt2@ are the same size.
\begin{tabbing}
@MMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMM@  \= \kill
@bad2 vs@                           \> $\exists k_{vs}.$ \\
@ = let flt  = filter p  vs@        \> $\forall k_{flt}.$ \\
@       flt2 = filter p' vs@        \> $\forall k_{flt2}.$ \\
@       mix  = map2   f  flt flt2@  \> $\exists k_{mix}.\ k_{mix} = k_{flt}$ \\
                                    \> $\wedge k_{mix} = k_{flt2} \wedge$ \\
@   in  mix@                        \> $true$                               \\
\end{tabbing}
Again, by transitivity of equality this constraint can be simplified to $\forall k_{flt}.\ \forall k_{flt2}.\ k_{flt} = k_{flt2}$.
It is easy to see that this constraint is unsatisfiable.
